Response to the defense feedback

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

\tool{} can estimate how
much information is leaked from each vulnerability. During the evaluation,
for each leakage site, \tool{} will stop once 1) it has 95\% confidence
that the error of the estimated leaked information is less than 1 bit,
which gives the leakage quantification a \emph{precision guarantee}, 
or 2) it cannot reach the termination condition after 10 minutes.  In
the latter case, it means \tool{} cannot estimate the amount of leakage with a
probabilistic guarantee. \tool{} times out on around 10\% reported side-channel leakage sites. We manually check these leakage sites and find most of them are quite severe.
We will present the details in the subsequent sections.

@@

During our evaluation, we find mbed TLS 2.5 and 2.15.1 have the same
implementation of AES\@. Our tool provides the same leakage report for both
versions. \tool{} identifies that most leakages are in function
\emph{mbedtls\_internal\_aes\_decrypt}. (Other leakage sites are in function
\emph{mbedtls\_aes\_setkey\_enc}.) All leakages are caused by the secret-dependent
memory accesses. Shown in Figure~\ref{mbedtls_aes}, there are seven leakage
sites in total. Leakage 1, 2, 3 are the same and leakage 4, 5, 6, 7 are the
same. They both use a pre-computed lookup table to speed up computation.
However, \tool{} reports leakage 1, 2, 3 typically leak more information (7.6 - 8.1 bits)
compared to leakage 4, 5, 6, 7 (4.0 bits). We check the source code and find leakage 1, 2,
3 use secret to access the lookup table \emph{RT0, RT1, RT2, RT3}, which is 8K
each. On the contrary, leakage 4, 5, 6, 7 each accesses a smaller lookup table
(2K). Therefore, leakage 4, 5, 6, 7 leak less information.

>>>>

\tool{} can estimate how
much information is leaked from each vulnerability. During the evaluation,
for each leakage site, \tool{} will stop once 1) it has $95\%$ confidence
that the error of the estimated leaked information is less than $1.0$ bit,
which gives the leakage quantification a \emph{precision guarantee}, 
or 2) it cannot reach the termination condition after $10$ minutes.  In
the latter case, it means \tool{} cannot estimate the amount of leakage with a
probabilistic guarantee. \tool{} times out on around $10\%$ reported side-channel leakage sites. We manually check these leakage sites and find most of them are quite severe.
We will present the details in the subsequent sections.

@@

During our evaluation, we find mbed TLS 2.5 and 2.15.1 have the same
implementation of AES\@. Our tool provides the same leakage report for both
versions. \tool{} identifies that most leakages are in function
\emph{mbedtls\_internal\_aes\_decrypt}. (Other leakage sites are in function
\emph{mbedtls\_aes\_setkey\_enc}.) All leakages are caused by the secret-dependent
memory accesses. Shown in Figure~\ref{mbedtls_aes}, there are seven leakage
sites in total. Leakage 1, 2, 3 are the same and leakage 4, 5, 6, 7 are the
same. They both use a pre-computed lookup table to speed up the computation.
However, \tool{} reports leakage 1, 2, 3 typically leak more information (7.6 - 8.1 bits)
compared to leakage 4, 5, 6, 7 (4.0 bits). We check the source code and find leakage 1, 2,
3 use secret to access the lookup table \emph{RT0, RT1, RT2, RT3}, which is 8K
each. On the contrary, leakage 4, 5, 6, 7 each accesses a smaller lookup table
(2K). Therefore, leakage 4, 5, 6, 7 leak less information.
